Childhood exposure to non-persistent endocrine disruptors, glucocorticosteroids, and neurodevelopment: A study based on the parametric g-formula

### 2024-02-07 output/paper/_tables.qmd
Table ratios for entire population and HELIX SC only. No by cohort, tho.

scores |>
  gtsummary::tbl_summary(
    by = "cohort"
  ) |>
  gtsummary::add_overall() |>
  gtsummary::as_gt() |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
**Participants derived glucocorticosteroids concentrations, by cohort and overall (HELIX subcohort; 2013-2016).**
:::

>>>>

# Entire population (1004)
desc_sums_all <- scores |>
  dplyr::select(-cohort) |>
  gtsummary::tbl_summary(
    statistic = list(
      gtsummary::all_continuous() ~ c(
        "{median} ({p25}, {p75}); {N_miss} ({p_miss})"
      )
    ),
    missing = "no",
    digits = dplyr::everything() ~ 1
  )

# Intersection with HELIX subcohort (976)
targets::tar_load(
  dplyr::contains("load"),
  store = "~/mounts/rstudioserver/data/data_paper3/_targets/_targetsRQ2/"
)
desc_sums_intersection <- create_steroid_scores(rq2_load_dat$outcome) |>
  dplyr::select(
    cortisol_production,
    cortisone_production,
    corticosterone_production
  ) |>
  tidylog::rename(
    "cortisol production" = "cortisol_production",
    "cortisone production" = "cortisone_production",
    "corticosterone production" = "corticosterone_production"
  ) |>
  gtsummary::tbl_summary(
    statistic = list(
      gtsummary::all_continuous() ~ c(
        "{median} ({p25}, {p75}); {N_miss} ({p_miss})"
      )
    ),
    missing = "no",
    digits = dplyr::everything() ~ 1
  )

gtsummary::tbl_merge(
  tbls = list(desc_sums_all, desc_sums_intersection)
) |>
  gtsummary::modify_spanning_header(
    dplyr::everything() ~ NA_character_
  ) |>
  gtsummary::as_gt() |>
  gt::tab_footnote(
    footnote = "Measurements available for the HELIX subcohort.",
    locations = gt::cells_column_labels(8)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
**Participants derived glucocorticosteroids concentrations, by cohort and overall (HELIX subcohort; 2013-2016).**
:::
